\documentclass[12pt, a4paper]{article}
\usepackage[a4paper, includeheadfoot, mag=1000, left=2cm, right=1.5cm, top=1.5cm, bottom=1.5cm, headsep=0.8cm, footskip=0.8cm]{geometry}
% Fonts
\usepackage{fontspec, unicode-math}
\setmainfont[Ligatures=TeX]{CMU Serif}
\setmonofont{CMU Typewriter Text}
\usepackage[english, russian]{babel}
% Indent first paragraph
\usepackage{indentfirst}
\setlength{\parskip}{5pt}
% Page headings
\usepackage{fancyhdr}
% Diagrams
\usepackage{graphicx}
% Code listing
\usepackage{listings}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{16pt}
\newfontfamily\namefont[Scale=1.2]{Gloria Hallelujah}
\fancyhead{}
% Use case template

\begin{document}

% Title page
\include{spectitlepage}

\section*{Assignment}
\subsection*{Linked list}
The program accepts an arbitrary number of integers through stdin or input file. What you have to do is
\begin{enumerate}
  \item Save them all in a linked list in reverse order.
  \item Write a function to compute the sum of elements in a linked list.
  \item Use this function to compute the sum of elements in the saved list.
  \item Write a function to output the n-th element of the list. If the list is too  short, signal about it.
  \item Free the memory allocated for the linked list.
\end{enumerate}

\subsection*{Higher-Order Functions}
In this assignment, we are going to implement several higher-order functions on linked lists, which should 
be familiar to those used to functional programming paradigm.

These functions are known under the names \texttt{foreach map map\_mut foldl}
\begin{enumerate}
  \item Save these integers in a linked list.
  \item Transfer all functions written in previous assignment into separate.h and c files. Do not forget to
  put an include guard!
  \item Implement \texttt{foreach;} using it, output the initial list to stdout twice: the first time, separate elements
  with spaces, the second time output each element on the new line.
  \item Implement \texttt{map;} using it, output the squares and the cubes of the numbers from list.
  \item Implement \texttt{foldl;} using it, output the sum and the minimal and maximal element in the list.
  \item Implement \texttt{map\_mut;} using it, output the modules of the input numbers.
  \item Implement \texttt{iterate;} using it, create and output the list of the powers of two.
  \item Implement a function bool \texttt{save(struct list* lst, const char* filename);}, which will write all elements of the list into a text file filename. It should return \texttt{true} in case the write is successful, \texttt{false} otherwise.
  \item Implement a function \texttt{bool load(struct list** lst, const char* filename);}, which will read all integers from a text file filename and write the saved list into *lst. It should return \texttt{true} in case the write is successful, \texttt{false} otherwise.
  \item Save the list into a text file and load it back using the two functions above. Verify that the save and load are correct.
  \item Implement a function bool \texttt{serialize(struct list* lst, const char* filename);}, which will write all elements of the list into a binary file filename. It should return \texttt{true} in case the write is successful, \texttt{false} otherwise.
  \item Implement a function \texttt{bool deserialize(struct list** lst, const char* filename);}, which will read all integers from a binary file filename and write the saved list into *lst. It should return \texttt{true} in case the write is successful, \texttt{false} otherwise.
  \item Serialize the list into a binary file and load it back using two functions above. Verify that the serialization and deserialization are correct.
  \item Free all allocated memory.
\end{enumerate}

\section*{Code listing}
Code listing is available in

https://github.com/johnny-keker/system-programming-languages/tree/master/lab4

\section*{Conclusion}
While compliting the assignment I wrote simple realization of linked list in C language and implemented some higher-order functions, such as
\texttt{foreach map map\_mut foldl}
\end{document}
